### 2021-07-08 docs/manuscript/manuscript.tex
Rephrase text

This study can help us to understand the mechanisms by which the GRNs work in
nature as modules that make part of genomes, and it also can provide guidance
in the construction of new synthetic GRNs in the field of synthetic biology.

We found the presence of network motifs in the set of GRNs produced by the
genetic algorithm. However, we also found a great diversity of network
topologies that could produce a striped gene expression pattern, where 615 out of
714 were multi-input topologies, showing that considering multiple
morphogen inputs allows to find different solution for the patterning
problem.\\

Robustness is an important feature of patterning mediated by morphogens, and
the GRNs involved can be selected in an evolutionary process not only by their final
steady state but also by their ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.
In our study, the most abundant topologies were
found to be part of highly connected clusters in the neutral network, and this fact
indicates that these topologies are both robust to quantitative changes in the
strength of interactions and diffusion and degradation parameters as well as to
qualitative changes in the topology itself. This, in principle, means that many
mechanisms for producing striped patterns are available and accessible to each
other through bridge topologies (\nameref{S6_Fig}), i.e.,
an organism can change between different GRNs (for example between
a Gierer-Meinhardt-like network to an Incoherent Feed-Forward Loop) without losing its
fitness, which allows to fine-tune the regulatory system according to its specific
needs. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable in the sense that they can produce
heritable variation of the expression pattern.\\

>>>>

In this work, we have conducted extensive computational explorations of small
GRNs with the capacity to generate a simple spatial pattern in a 1-D
morphogenetic field. Our findings shed new light on regulatory rules and
dynamical mechanisms that  GRNs observed in nature could potentially
implement to achieve fundamental spatio-temporal tasks, which might
serve as guidance for future synthetic biology implementations.

Overall, based on our extensive search space exploration we were able to identify
a great variety of pattern-forming GRN topologies  with distinctive and often
widely shared building blocks (network motifs), which are likely to confer on
each topology the ability to achieve specific regulatory tasks in a semi-autonomous
manner. However, we also found a great diversity of network
topologies that could produce a striped gene expression pattern, where 615 out of
714 were multi-input topologies, showing that considering multiple
morphogen inputs allows to find different solution for the patterning
problem. Most importantly, we found that this ensemble of pattern-forming GRNs
tend to form a highly connected meta-graph, which highlights at a very high level
emergent properties, such as robustness and evolvability, of complex biological
systems \cite{kitano2004}.\\

Robustness is a defining feature of any developmental patterning process,
and our results suggests that the underlying morphogen interpretation
mechanisms (GRNs) are highly accessible through exploration of the
topology space constrained not only by selection for their final steady state,
but also by their ability to buffer noise~\cite{lo_robust_2015, exelby_2021}.

In our study, the most abundant topologies were found forming highly
connected clusters in a so-called neutral network of genotypes,
implying that the corresponding GRN topologies would tend to be robust
to quantitative changes in the strength of regulatory interactions, diffusion and
degradation parameters, as well as to qualitative changes in the topology
itself. In essence, such organization could be seen as an intrinsic evolutionary
property of GRNs that facilitates the coexistence of robustness and
evolvability~\cite{wagner_robustness_2008}. For instance, bridge topologies
in the neutral network connect distinct classes of pattern-forming
GRNs~(\nameref{S6_Fig}), which suggests that an organism could switch
between different GRNs (for example between a Gierer-Meinhardt-like network
to an Incoherent Feed-Forward Loop) with minimal fitness costs. This high-level
property of the neutral network of topologies could thus facilitate the fine-tuning
of the regulatory systems through genetic modifications in order to meet specific functional requirements under selective pressures.

 which allows to fine-tune the regulatory system according to its specific
needs. As robustness and evolvability are
not mutually exclusive properties~\cite{wagner_robustness_2008}, it is likely
that these topologies are also evolvable in the sense that they can produce
heritable variation of the expression pattern.\\
